Numerical experiment investigating the influence of drag on trajectory patterns of floating macroalgae

### 2021-05-06 thesis_chapter_3.Rmd
chp3 graphs touchups

@@

The mean trajectories of kelp particles were different compared to the mean trajectory of passive particles for April (Austral autumn). Mean trajectories for kelp particles with different cross-sectional areas exposed to only hydrodynamic drag traveled further northward compared to the passive particles (Figure 3C-D). The mean trajectories of virtual kelp particles with different cross-sectional area types and a combination of wind and hydrodynamic drag flowed further north-westward compared to the passive particles. Across all simulations for April, the end locations were different, and hydrodynamic only kelp particles traveled less distance compared to kelp particles with both wind and hydrodynamic drag. Differences in mean trajectories between kelp and passive particles were also evident in the July (Austral winter) simulations (see Figure 3E-F). Mean trajectories of passive particles flowed north-westward, while kelp particles across cross-sectional areas and exposed to only hydrodynamic drag initially flowed in a southerly direction and then flowed westward offshore, resulting in entrainment within an eddy. Similar behavior is evident when comparing passive particles with kelp particles exposed to both hydrodynamic and wind drag. In the combined hydrodynamic and water drag scenarios, and across cross-sectional areas; kelp particles traveled initially southward and then westward offshore and also becoming entrained in an eddy. In the October (Austral spring) simulations, differences in end locations were evident between passive and kelp particles across cross-sectional areas and drag scenarios (Figure 3F-G). Mean Trajectory of kelp particles with different cross-sectional areas and exposed to only hydrodynamic drag stop a greater distance from the release site compared to the passive particles. This was also evident when comparing kelp particles with different cross-sectional areas and exposure to wind and hydrodynamic drag with passive particles, with the end location a further from the release location. In both the April and October simulations all particles flowed north-westward, while in winter the mean trajectory resulted in entrainment within an eddy.

@@

waterdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  geom_path(data = total_mean_water, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  geom_path(data = total_mean_ww, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_April <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  geom_path(data = total_mean_water_April, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_April <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill ="grey") +
  geom_path(data = total_mean_ww_April, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  geom_path(data = total_mean_water_July, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  geom_path(data = total_mean_ww_July, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_Oct <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0,     colour = "black",     fill = "grey") +
  geom_path(data = total_mean_water_Oct, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme_bw()

wwdrag_plot_Oct <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0,     colour = "black",     fill = "grey") +
  geom_path(data = total_mean_ww_Oct, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme_bw()

@@

ggarrange(waterdrag_plot, wwdrag_plot, waterdrag_plot_April, wwdrag_plot_April, waterdrag_plot_July, wwdrag_plot_July, waterdrag_plot_Oct, wwdrag_plot_Oct, ncol = 2, nrow = 4, font.label = list(size = 11, face = "bold"), common.legend = FALSE, legend = c("bottom"), labels = "AUTO", align = "hv")
```

@@

heatmap_RK4 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = p_RK4, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 1100)) +
  geom_path(data = p_RK4_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis",limits = c(1, 1100)) +
  geom_path(data = Min_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  #ggtitle("H100W100") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H095_W05, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis",limits = c(1, 1100)) +
  geom_path(data = Min_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  #ggtitle("H095W05") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H090_W10, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis",limits = c(1, 1100)) +
  geom_path(data = Min_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  #ggtitle("H090W10") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H085_W15, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 1100)) +
  geom_path(data = Min_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  #ggtitle("H085W15") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Mean_Kfloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 1100)) +
  geom_path(data = Mean_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Mean_KFloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app1, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H095_W05, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  scale_fill_continuous(type = "viridis", limits = c(1, 1100)) +
  geom_path(data = Mean_KFloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Mean_KFloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H090_W10, bins = 80, aes(x = lon, y = lat), legend = TRUE) +
  scale_fill_continuous(type = "viridis", limits = c(1, 1100)) +
  geom_path(data = Mean_KFloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Mean_KFloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H085_W15, bins = 80, aes(x = lon, y = lat), legend = TRUE) +
  scale_fill_continuous(type = "viridis", limits = c(1, 1100)) +
  geom_path(data = Mean_KFloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Max_KFloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat), legend = TRUE) +
  scale_fill_continuous(type = "viridis", limits = c(1, 1100)) +
  geom_path(data = Max_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

>>>>

load("map/south_africa_coast_hi_res.Rdata")
load("map/sa_bathy.RData")

@@

The mean trajectories of kelp particles were different compared to the mean trajectory of passive particles for April (Austral autumn). Mean trajectories for kelp particles with different cross-sectional areas exposed to only hydrodynamic drag traveled further northward compared to the passive particles (Figure 3C-D). The mean trajectories of virtual kelp particles with different cross-sectional area types and a combination of wind and hydrodynamic drag flowed further north-westward compared to the passive particles. Across all simulations for April, the end locations were different, and hydrodynamic only kelp particles traveled less distance compared to kelp particles with both wind and hydrodynamic drag. Differences in mean trajectories between kelp and passive particles were also evident in the July (Austral winter) simulations (Figure 3E-F). Mean trajectories of passive particles flowed north-westward, while kelp particles across cross-sectional areas and exposed to only hydrodynamic drag initially flowed in a southerly direction and then flowed westward offshore, resulting in entrainment within an eddy. Similar behavior is evident when comparing passive particles with kelp particles exposed to both hydrodynamic and wind drag. In the combined hydrodynamic and water drag scenarios, and across cross-sectional areas; kelp particles traveled initially southward and then westward offshore and also becoming entrained in an eddy. In the October (Austral spring) simulations, differences in end locations were evident between passive and kelp particles across cross-sectional areas and drag scenarios (Figure 3F-G). Mean Trajectory of kelp particles with different cross-sectional areas and exposed to only hydrodynamic drag stop a greater distance from the release site compared to the passive particles. This was also evident when comparing kelp particles with different cross-sectional areas and exposure to wind and hydrodynamic drag with passive particles, with the end location a further from the release location. In both the April and October simulations all particles flowed north-westward, while in winter the mean trajectory resulted in entrainment within an eddy.

@@

waterdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_path(data = total_mean_water, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

wwdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_path(data = total_mean_ww, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

@@

waterdrag_plot_April <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_path(data = total_mean_water_April, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

wwdrag_plot_April <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill ="grey") +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_path(data = total_mean_ww_April, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

@@

waterdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_path(data = total_mean_water_July, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

wwdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_path(data = total_mean_ww_July, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

@@

waterdrag_plot_Oct <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0,     colour = "black",     fill = "grey") +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_path(data = total_mean_water_Oct, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

wwdrag_plot_Oct <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0,     colour = "black",     fill = "grey") +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_path(data = total_mean_ww_Oct, aes(x = lon, y = lat, linetype = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(linetype=guide_legend(title="Simulation")) +
  coord_fixed(ratio=1, clip = "on", xlim = c(11, 20), ylim = c(-36, -28)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

@@

ggarrange(waterdrag_plot, wwdrag_plot, waterdrag_plot_April, wwdrag_plot_April, waterdrag_plot_July, wwdrag_plot_July, waterdrag_plot_Oct, wwdrag_plot_Oct, ncol = 2, nrow = 4, font.label = list(size = 12, face = "bold"), common.legend = FALSE, legend = c("bottom"), labels = c("A","B","C","D","E","F","G", "H"), align = "hv")

ggsave(filename = "figure_3.jpg", plot = last_plot(), path = "figures/chapter_3/", height = 10, width = 10, dpi = 300, scale = 2.0)
```

@@

load("map/south_africa_coast_hi_res.Rdata")
load("map/sa_bathy.RData")

heatmap_RK4 <- ggplot() +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_hex(data = p_RK4, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 1100)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = "gray") +
  geom_path(data = p_RK4_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("1") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

heatmap_Min_Kfloat_H100_W00 <- ggplot() +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_hex(data = Min_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis",limits = c(1, 1100))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = "gray") +
  geom_path(data = Min_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("2") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

heatmap_Min_Kfloat_H095_W05 <- ggplot() +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_hex(data = Min_Kfloat_H095_W05, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis",limits = c(1, 1100)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = "gray") +
  geom_path(data = Min_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  ggtitle("3") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

heatmap_Min_Kfloat_H090_W10 <- ggplot() +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_hex(data = Min_Kfloat_H090_W10, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis",limits = c(1, 1100)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = "gray") +
  geom_path(data = Min_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("4") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

heatmap_Min_Kfloat_H085_W15 <- ggplot() +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_hex(data = Min_Kfloat_H085_W15, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 1100))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = "gray") +
  geom_path(data = Min_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("5") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

heatmap_Mean_Kfloat_H100_W00 <- ggplot() +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_hex(data = Mean_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  
  scale_fill_continuous(type = "viridis", limits = c(1, 1100))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = "gray") +
  geom_path(data = Mean_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("6") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

heatmap_Mean_KFloat_H095_W05 <- ggplot() +
  #geom_bin2d(data = k_app1, bins = 80, aes(x = lon, y = lat)) +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_hex(data = Mean_KFloat_H095_W05, bins = 80, aes(x = lon, y = lat), legend = TRUE) +  scale_fill_continuous(type = "viridis", limits = c(1, 1100))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = "gray") +
  geom_path(data = Mean_KFloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("7") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

heatmap_Mean_KFloat_H090_W10 <- ggplot() +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_hex(data = Mean_KFloat_H090_W10, bins = 80, aes(x = lon, y = lat), legend = TRUE) +
  scale_fill_continuous(type = "viridis", limits = c(1, 1100))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = "gray") +
  geom_path(data = Mean_KFloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("8") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

heatmap_Mean_KFloat_H085_W15 <- ggplot() +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_hex(data = Mean_KFloat_H085_W15, bins = 80, aes(x = lon, y = lat), legend = TRUE) +
  scale_fill_continuous(type = "viridis", limits = c(1, 1100))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = "gray") +
  geom_path(data = Mean_KFloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("9") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))
